### 2022-03-03 README.Rmd
Updated formatting.
Update .gitignore, Dockerfile, renv.lock, and the compendium package description and readme.

This repository contains the data and code for our submitted manuscript:

> `r paste(manuscript1$authors, "(submitted)", manuscript1$title)`

@@

> Henning Teickner and Klaus-Holger Knorr, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for "`r manuscript1_yaml$title`"_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source documents
    needed to reproduce the manuscript, including figures and tables. The main 
    script is [001-paper-main.Rmd](analysis/paper/001-paper-main.Rmd). Additional scripts are:
        - [002-paper-m-original-models.Rmd](analysis/paper/002-paper-m-original-models.Rmd): Computes the original models used in @Hodgkins.2018 and models with the same model structure, but as Bayesian models.  
        - [003-paper-m-gaussian-beta.Rmd](analysis/paper/003-paper-m-gaussian-beta.Rmd): Computes models assuming a Beta distribution for holocellulose and Klason lignin contents and compares them to the original models.
        - [004-paper-m-reduce-underfitting.Rmd](analysis/paper/004-paper-m-reduce-underfitting.Rmd): Extents the Beta regression models by including additional variables (additional peaks) or using a different approach (using measured spectral intensities of binned spectra instead of extracted peaks), and validates these models using LOO-CV.
        - [005-paper-m-minerals.Rmd](analysis/paper/005-paper-m-minerals.Rmd): Uses the models from `003-paper-m-gaussian-beta.Rmd` to test how accurate a model for holocellulose content is which is also calibrated on training samples with higher mineral contents.
        - [006-paper-m-prediction-domain.Rmd](analysis/paper/006-paper-m-prediction-domain.Rmd): Analyzes the prediction domain [@Wadoux.2021] of the original models and the modified models and identifie under which conditions models extrapolate for peat and vegetation smaples from @Hodgkins.2018.
        - [007-paper-m-prediction-differences.Rmd](analysis/paper/007-paper-m-prediction-differences.Rmd): Compares predictions for the training data and the peat and vegetation data from @Hodgkins.2018 for the original models from @Hodgkins.2018 and the modified models from `004-paper-m-reduce-underfitting.Rmd`.
        - [008-paper-supplementary.Rmd](analysis/paper/008-paper-supplementary.Rmd): Computes supplementary analyses and figures.
  - [:file\_folder: data](/analysis/data): Data used in the analysis. Note that raw data is not stored in [:file\_folder: raw_data](/analysis/data/raw_data) (empty folder), but in [:file\_folder: /inst/extdata](/inst/extdata). [:file\_folder: derived_data](/analysis/data/derived_data) contains derived data computed from the scripts. The raw data are derived from @Hodgkins.2018.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations (empty folder).

@@

- `README.md`/`README.Rmd`: Readme for the compendium.  
- `DESCRIPTION`: The R package DESCRIPTION file for the compendium.  
- `NAMESPACE`: The R package NAMESPACE file for the compendium.  
- `LICENSE.md`: Details on the license for the code in the compendium.  
- `CONTRIBUTING.md` and `CONDUCT.md`: Files with information on how to contribute to the compendium.  
- `Dockerfile`: Dockerfile to build a Docker image for the compendium.  
- `.Rbuildignore`, `.gitignore`, `.dockerignore`: Files to ignore during R package building, to ignore by Git, and to ignore while building a Docker image, respectively.  
- `renv.lock`: renv lock file (Lists all R package dependencies and versions and can be used to restore the R package library using renv). `renv.lock` was created by running     `renv::snapshot()` in the R package directory and it uses the information included in the `DESCRIPTION` file.  
- `.Rprofile`: Code to run upon opening the R-project.  
- `R`, `man`, `inst`, `data-raw`, `data`, `src`: Default folders for making the R package run.

  - Folder `inst/extdata`: Folder with the raw data used for the analyses. All files in this folder are derived from @Hodgkins.2018.

@@

Running the whole script takes about two hours and occupies additional disk space of ~2 Gb.

@@

The [Dockerfile](Dockerfile) provides instructions how to build a Docker image from the Dockerfile and how to run the image in a Docker container. It occupies disk space of ~5 Gb.

>>>>

This repository contains the data and code for our two manuscripts (in preparation):

> `r paste(manuscript1$authors, "(in preparation):", manuscript1$title)`

> `r paste(manuscript2$authors, "(in preparation):", manuscript2$title)`

@@

> Henning Teickner and Klaus-Holger Knorr, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for "`r manuscript1_yaml$title`" and "`r manuscript2_yaml$title`"_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

- [:file\_folder: paper](/analysis/paper): R Markdown source documents needed to reproduce the manuscript, including figures and tables. The main script is [001-paper-main.Rmd](analysis/paper/001-paper-main.Rmd). This script produces both manuscripts and the corresponding supplementary information. Additional scripts are:  
    - [002-paper-m-original-models.Rmd](analysis/paper/002-paper-m-original-models.Rmd): Computes the original models used in @Hodgkins.2018 and models with the same model structure, but as Bayesian models.  
    - [003-paper-m-gaussian-beta.Rmd](analysis/paper/003-paper-m-gaussian-beta.Rmd): Computes models assuming a Beta distribution for holocellulose and Klason lignin contents and compares them to the original models.
    - [004-paper-m-reduce-underfitting.Rmd](analysis/paper/004-paper-m-reduce-underfitting.Rmd): Extents the Beta regression models by including additional variables (additional peaks) or using a different approach (using measured spectral intensities of binned spectra instead of extracted peaks), and validates these models using LOO-CV.
    - [005-paper-m-minerals.Rmd](analysis/paper/005-paper-m-minerals.Rmd): Uses the models from `003-paper-m-gaussian-beta.Rmd` to test how accurate a model for holocellulose content is which is also calibrated on training samples with higher mineral contents.
    - [006-paper-m-prediction-domain.Rmd](analysis/paper/006-paper-m-prediction-domain.Rmd): Analyzes the prediction domain [@Wadoux.2021] of the original models and the modified models and identifie under which conditions models extrapolate for peat and vegetation smaples from @Hodgkins.2018.
    - [007-paper-m-prediction-differences.Rmd](analysis/paper/007-paper-m-prediction-differences.Rmd): Compares predictions for the training data and the peat and vegetation data from @Hodgkins.2018 for the original models from @Hodgkins.2018 and the modified models from `004-paper-m-reduce-underfitting.Rmd`.
    - [008-paper-supplementary.Rmd](analysis/paper/008-paper-supplementary.Rmd): Computes supplementary analyses and figures for the first manuscript.
    - [001-reply-main.Rmd](analysis/paper/001-reply-main.Rmd): This is the main script for manuscript 2. It is run from within `001-paper-main.Rmd` and produces the supplementary information for manuscript 2.
    - [002-reply-main.Rmd](analysis/paper/002-reply-main.Rmd): This script produces the document for manuscript 2. It is run from within `001-reply-main.Rmd`.

- [:file\_folder: data](/analysis/data): Data used in the analysis. Note that raw data is not stored in [:file\_folder: raw_data](/analysis/data/raw_data) (empty folder), but in [:file\_folder: /inst/extdata](/inst/extdata). [:file\_folder: derived_data](/analysis/data/derived_data) contains derived data computed from the scripts. The raw data are derived from @Hodgkins.2018.

- [:file\_folder: stan_models](/analysis/stan_models): The Stan model used in `001-reply-main.Rmd`.

@@

- `README.md`/`README.Rmd`: Readme for the compendium.  
- `DESCRIPTION`: The R package DESCRIPTION file for the compendium.  
- `NAMESPACE`: The R package NAMESPACE file for the compendium.  
- `LICENSE.md`: Details on the license for the code in the compendium.  
- `CONTRIBUTING.md` and `CONDUCT.md`: Files with information on how to contribute to the compendium.  
- `Dockerfile`: Dockerfile to build a Docker image for the compendium.  
- `.Rbuildignore`, `.gitignore`, `.dockerignore`: Files to ignore during R package building, to ignore by Git, and to ignore while building a Docker image, respectively.  
- `renv.lock`: renv lock file (Lists all R package dependencies and versions and can be used to restore the R package library using renv). `renv.lock` was created by running     `renv::snapshot()` in the R package directory and it uses the information included in the `DESCRIPTION` file.  
- `.Rprofile`: Code to run upon opening the R-project.  
- `R`, `man`, `inst`, `data-raw`, `data`, `src`: Default folders for making the R package run.
- Folder `inst/extdata`: Folder with the raw data used for the analyses. All files in this folder are derived from @Hodgkins.2018.

@@

Running the whole script takes about 12 hours and occupies additional disk space of ~2 Gb.

@@

The [Dockerfile](Dockerfile) provides instructions how to build a Docker image from the Dockerfile and how to run the image in a Docker container. It occupies disk space of ~6 Gb.
